|

### 2021-12-13 front-and-back-matter/_acknowledgements.Rmd
Admin

First and foremost, I would like to thank my supervisors - Julian Higgins, Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their support over the past three years. Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews. Sharen O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support. Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.

@@

Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
<<github>>. A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.

>>>>

First and foremost, I would like to thank my supervisors - Julian Higgins, Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their support over the past three years. Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews. Sharen Hockey-O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support. Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.

@@

Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
<<github>> A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.
